---
title: "Practice 4.1"
author: "Wei-Ting Sun"
date: "2024-10-20"
output: html_document
---
### Use the `iris` dataset to reproduce the plot 
```{r}
data("iris")
```
I didn't know whether I need to reproduce the plot by `pairs` or not, and awfully I cannot make it successfully by `pairs`. So I reproduce the plot by `plot` first.

```{r, warning=FALSE, message=FALSE}
d.setosa<-iris[iris$Species=='setosa',]
d.versicolor<-iris[iris$Species=='versicolor',]  
d.virginica<-iris[iris$Species=='virginica',] 
  
x_range <- range(1, iris$Petal.Length)
y_range <- range(0, iris$Petal.Width)

plot(d.setosa$Petal.Length, d.setosa$Petal.Width,
     xlim=x_range ,ylim=y_range, main="Petal width vs. length",
     xlab="Petal length (cm)", ylab="Petal width (cm)", axes=FALSE)
lines(d.versicolor$Petal.Length, d.versicolor$Petal.Width,
      type = "p", pch=2, col="red", xlim=x_range ,ylim=y_range, axes=FALSE, ann=FALSE)
lines(d.virginica$Petal.Length, d.virginica$Petal.Width,
      type = "p", pch=3, col="green", xlim=x_range ,ylim=y_range, axes=FALSE, ann=FALSE)

axis(1, at=seq(1,7))
axis(2, at=seq(0.5, 2.5,by=0.5))
box()

legend("topleft", legend=c("setosa","versicolor","virginica"),
       col=c("black","red","green"), pch=1:2:3 )

abline(lm(iris$Petal.Width ~ iris$Petal.Length), col="black")
text(5, 0.5, paste("R =", round(cor(iris$Petal.Length, iris$Petal.Width), 2)))

# Your code could be way shorter, you will see it tomorrow
# You can also try to recycle the R from your lm. Try:
# model<-lm(iris$Petal.Width ~ iris$Petal.Length)
# r2_value <- summary(model)$r.squared
# text(5.5, 0.5, labels = paste("R = ", round(sqrt(r2_value), 2)), pos = 4)

```
I tried to use `pairs` to make a plot, but I was not sure about what I made :( 
VD: I was just asking to explore what you can do using `pairs`. You did well below.


```{r, warning=FALSE, message=FALSE}
pairs(iris[1:4], 
      col=c("black", "red", "green")[iris$Species], 
      pch=c(1, 2, 3)[iris$Species], 
      main="Petal width vs. length")
```

Finally, I save these plot in pdf format
```{r, warning=FALSE, message=FALSE}
pdf(file = "outputs/Scatter_plot_1.pdf", paper = "A4r")

d.setosa<-iris[iris$Species=='setosa',]
d.versicolor<-iris[iris$Species=='versicolor',]  
d.virginica<-iris[iris$Species=='virginica',] 
  
x_range <- range(1, iris$Petal.Length)
y_range <- range(0, iris$Petal.Width)

plot(d.setosa$Petal.Length, d.setosa$Petal.Width,
     xlim=x_range ,ylim=y_range, main="Petal width vs. length",
     xlab="Petal length (cm)", ylab="Petal width (cm)", axes=FALSE)
lines(d.versicolor$Petal.Length, d.versicolor$Petal.Width,
      type = "p", pch=2, col="red", xlim=x_range ,ylim=y_range, axes=FALSE, ann=FALSE)
lines(d.virginica$Petal.Length, d.virginica$Petal.Width,
      type = "p", pch=3, col="green", xlim=x_range ,ylim=y_range, axes=FALSE, ann=FALSE)

axis(1, at=seq(1,7))
axis(2, at=seq(0.5, 2.5,by=0.5))
box()

legend("topleft", legend=c("setosa","versicolor","virginica"),
       col=c("black","red","green"), pch=1:2:3 )

abline(lm(iris$Petal.Width ~ iris$Petal.Length), col="black")
text(5, 0.5, paste("R =", round(cor(iris$Petal.Length, iris$Petal.Width), 2)))

dev.off()

pdf(file = "outputs/Scatter_plot_2.pdf", paper = "A4r")

pairs(iris[1:4], 
      col=c("black", "red", "green")[iris$Species], 
      pch=c(1, 2, 3)[iris$Species], 
      main="Petal width vs. length")

dev.off()
```
